Bee visitation, pollination service, and plant yield in commodity and hybrid seed canola

### 2023-01-19 Manuscript/manuscript_files/supplemental.tex
Worked on revisions

%%%%%%%%%% Merge with supplemental materials %%%%%%%%%%
%%%%%%%%%% Prefix a "S" to all equations, figures, tables and reset the counter %%%%%%%%%%
\setcounter{equation}{0} %Resets page, eqn, figure, table numbers
\setcounter{figure}{0}
\setcounter{table}{0}
%\setcounter{page}{1} 
\makeatletter
\renewcommand{\theequation}{S\arabic{equation}} %Adds S to the front of references
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thetable}{S\arabic{table}}
\renewcommand{\bibnumfmt}[1]{[S#1]}
\renewcommand{\citenumfont}[1]{S#1}
%\pagenumbering{gobble}

\clearpage
\section*{Appendix A: Additional figures and tables}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.9\textwidth,keepaspectratio=true]{../Figures/FieldLocations.png}
    \caption{Map of sampled fields, showing locations of 29 commodity canola fields (14 during 2014, 15 during 2015), and 35 seed canola fields (15 during 2015, 20 during 2016). Seed canola is grown only in southern Alberta, while commodity canola is grown across both the northern and southern regions.}
    \label{fig:fieldMap}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth,keepaspectratio=true]{seedfieldBays.jpg}
    \caption[Hybrid seed field production field near Rainer, AB]{Hybrid seed field near Rainer, AB, showing the outlines of male and female bays in the foreground, with orange leafcutter bee shelters stationed throughout the field. The linear structure on the horizon is the central-pivot irrigation sprinkler.}
    \label{fig:seedfieldPhoto}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth,keepaspectratio=true]{seedfieldPlots.png}
    \caption[Plot arrangement for surveys in hybrid seed fields]{Plot arrangement for surveys in hybrid seed fields, showing hypothetical arrangement of leafcutter shelters ($\Delta$), and male-fertile (\Hermaphrodite) and female bays (\Female) at 5m from the edge of the field. Plots were placed along a transect (dashed line) from the field edge nearest to the set of honey bee hives. Plots were placed side-by-side in the male bay and edge of the female bay (``edge" plots), and at the 5m and 400m distances, an additional plot was placed in the centre of the female bay (``centre" plots). Note: this figure shows a small section of a much larger circular field.}
    \label{fig:seedfieldPlots}
\end{figure}

\begin{table}[h]
\caption{Summary of variables used in structural equation models.}
\centering
\begin{tabular}{l|l|r|r|r|r|r}
\hline
Field Type & Variable & Mean & Median & SD & Min & Max\\
\hline
 & Number of hives & 14.80 & 0.00 & 17.03 & 0.00 & 40.00\\
\cline{2-7}
 & Distance to edge (m) & 137.48 & 20.00 & 195.02 & 1.00 & 500.00\\
\cline{2-7}
 & HB visitation (hr$^{-1}$) & 10.31 & 0.00 & 28.80 & 0.00 & 218.18\\
\cline{2-7}
 & Flower density (m$^2$) & 470.33 & 448.00 & 231.32 & 52.00 & 1684.00\\
\cline{2-7}
 & Pollen per stigma & 293.33 & 155.00 & 385.04 & 0.00 & 3891.00\\
\cline{2-7}
 & Plant density (m$^2$) & 3.77 & 3.77 & 0.48 & 1.79 & 5.02\\
\cline{2-7}
 & Plant vegetative mass (g) & 18.15 & 14.32 & 14.07 & 0.77 & 107.66\\
\cline{2-7}
 & Plant seed mass (g) & 6.87 & 5.46 & 5.97 & 0.01 & 47.90\\
\cline{2-7}
 & Harvest index (g/g) & 0.38 & 0.37 & 0.16 & 0.00 & 1.89\\
\cline{2-7}
 & Flowers per plant & 196.09 & 156.50 & 150.96 & 13.00 & 1094.00\\
\cline{2-7}
 & Pods per plant & 143.15 & 112.00 & 114.64 & 5.00 & 892.00\\
\cline{2-7}
 & Seeds per pod & 22.96 & 23.60 & 4.97 & 4.60 & 35.40\\
\cline{2-7}
\multirow{-13}{*}{\raggedright\arraybackslash Commodity} & Seed size (mg) & 2.74 & 2.73 & 0.80 & 0.39 & 5.35\\
\cline{1-7}
 & Distance to edge (m) & 162.70 & 100.00 & 146.18 & 3.00 & 400.00\\
\cline{2-7}
 & Distance to LCB shelter (m) & 33.51 & 31.00 & 24.63 & 2.00 & 190.00\\
\cline{2-7}
 & HB visitation (hr$^{-1}$) & 112.79 & 24.00 & 187.30 & 0.00 & 1290.00\\
\cline{2-7}
 & LCB visitation (hr$^{-1}$) & 76.15 & 12.00 & 144.88 & 0.00 & 1272.00\\
\cline{2-7}
 & Bay Edge/Centre & 0.13 & 0.00 & 0.34 & 0.00 & 1.00\\
\cline{2-7}
 & Flower density (m$^2$) & 495.02 & 432.00 & 303.35 & 24.00 & 2686.40\\
\cline{2-7}
 & Pollen per stigma & 21.76 & 7.00 & 42.53 & 0.00 & 578.00\\
\cline{2-7}
 & Plant density (m$^2$) & 3.58 & 3.64 & 0.46 & 2.40 & 4.49\\
\cline{2-7}
 & Plant vegetative mass (g) & 30.32 & 25.19 & 21.16 & 1.18 & 144.32\\
\cline{2-7}
 & Plant seed mass (g) & 9.50 & 7.54 & 7.90 & 0.02 & 60.77\\
\cline{2-7}
 & Harvest index (g/g) & 0.32 & 0.33 & 0.15 & 0.00 & 1.21\\
\cline{2-7}
 & Flowers per plant & 461.32 & 362.50 & 326.59 & 26.00 & 2712.00\\
\cline{2-7}
 & Pods per plant & 299.41 & 244.50 & 207.68 & 10.00 & 1410.00\\
\cline{2-7}
 & Seeds per pod & 16.40 & 16.60 & 5.52 & 1.80 & 30.60\\
\cline{2-7}
\multirow{-15}{*}{\raggedright\arraybackslash Seed} & Seed size (mg) & 3.43 & 3.42 & 0.88 & 1.04 & 5.59\\
\hline
\end{tabular}

\label{tab:dataSummary}
\end{table}

@@

\begin{table}[h]
  \caption{Number of flower visitors recorded over a total of 44.8 hours of observation in commodity fields (2014 and 2015), and 46.9 hours of observation in the seed fields (2015 and 2016). ``Fly" refers to larger calyptrate muscoid flies (families Muscidae, Anthomyiidae, Caliphoridae), while ``Hover fly" refers to Syrphid flies. ``Other bee" included Halictid and Andrenid bees, while ``Bumble bee" was \textit{Bombus} spp. ``Butterfly" refers to all visiting Lepidopterans, mostly Pierids.}
  \centering
    \begin{tabular}{r|r|l|r|l}
     & \multicolumn{2}{c|}{Commodity fields} & \multicolumn{2}{c}{Seed fields} \\ \cline{2-5}
    Taxon & Visits & \% & Visits & \% \\ \hline
    Honey bee & 470 & 53.5 & 4850 & 77.1 \\
    Fly & 222 & 25.3 & 74 & 0.878 \\
    Hover fly & 94 & 10.7 & 151 & 1.79 \\
    Other bee & 47 & 5.35 & 30 & 0.356 \\
    Bumble bee & 25 & 2.85 & 0 & 0 \\
    Butterfly & 16 & 1.82 & 0 & 0 \\
    Leafcutter bee & 4 & 0.456 & 1675 & 19.9 \\
    % \hline
    % Total & 828 & - & 6780 & - \\
    \end{tabular}
    \label{tab:propVisitors}
\end{table}

\begin{table}[h]
\caption[Foraging behaviours of honey bees on commodity and seed canola flowers]{Foraging behaviours of honey bees on commodity and seed canola flowers, recorded during 2015. ``Top" (top-working) indicates that the bee inserted their proboscis down between the petals from the top of the flower, while ``side" (side-working) indicates that the bee fed from the side of the flower and did not contact the anthers or stigma. Pollen foragers had pollen visible on their corbicula, while nectar foragers had none.}
\begin{tabular}{r|r|l|r|l|r|l}
               & \multicolumn{2}{c|}{Commodity fields} & \multicolumn{2}{c|}{Seed fields (female bay)} & \multicolumn{2}{c}{Seed fields (male bay)} \\ \cline{2-7}
               & Top & Side & Top & Side & Top & Side           \\ \hline
Pollen forager & 44 & 2 & 12 & 0 & 115 & 0 \\
Nectar forager & 75 & 138 & 832 & 24 & 428 & 242 \\
% Total & 119 & 140 & 844 & 24 & 543 & 242
\end{tabular}
\label{tab:sideWorking}
\end{table}

@@

\label{tab:commCoefs}

@@

\label{tab:seedCoefs}

@@

>>>>

\documentclass[12pt]{article} % use larger type; default would be 10pt

\usepackage[utf8]{inputenc} % set input encoding (not needed with XeLaTeX)
\usepackage{geometry} % to change the page dimensions
\geometry{margin=1in} % for example, change the margins to 2 inches all round
\usepackage{graphicx} % support the \includegraphics command and options
\usepackage{booktabs} % for much better looking tables
\usepackage{array} % for better arrays (eg matrices) in maths
\usepackage{paralist} % very flexible & customizable lists (eg. enumerate/itemize, etc.)
\usepackage{verbatim} % adds environment for commenting out blocks of text & for better verbatim
\usepackage{subfig} % make it possible to include more than one captioned figure/table in a single float
\usepackage[round]{natbib} % Natural science bibliography package
\usepackage{pdflscape} %Landscape pages
\usepackage{amsmath} %Mathematics 
\usepackage{hyperref} %URLs and Hyperlinks
\hypersetup{hidelinks=true} %Turns off coloured links
\usepackage{longtable} %Multi-page tables
\usepackage{multirow} %Better tables
\usepackage{marvosym} %Male/female/hermaphrodite symbols
\usepackage{caption} %Add captions to non-floats
\usepackage{calc} %Simple arithmetic for arguments
\usepackage{ifthen} %Allows if-then statements
\usepackage[breakable]{tcolorbox} %Allows boxes to be made, and allows boxes to be breakable
\usepackage{capt-of} %Allows captions outside of float environments
\usepackage{setspace} %Double/1.5 spacing
\usepackage{multirow} %Multirow tables
\usepackage{sectsty}
\allsectionsfont{\sffamily\mdseries\upshape}

%%%%%%%%%% Prefix a "S" to all equations, figures, tables and reset the counter %%%%%%%%%%
\setcounter{equation}{0} %Resets page, eqn, figure, table numbers
\setcounter{figure}{0}
\setcounter{table}{0}
\makeatletter
\renewcommand{\theequation}{S\arabic{equation}} %Adds S to the front of references
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thetable}{S\arabic{table}}
\renewcommand{\bibnumfmt}[1]{[S#1]}
\renewcommand{\citenumfont}[1]{S#1}

\begin{document}

\section*{Appendix A: Additional figures and tables}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.9\textwidth,keepaspectratio=true]{FieldLocations.png}
    \caption{Map of sampled fields, showing locations of 29 commodity canola fields (14 during 2014, 15 during 2015), and 35 seed canola fields (15 during 2015, 20 during 2016). Seed canola is grown only in southern Alberta, while commodity canola is grown across both the northern and southern regions.}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth,keepaspectratio=true]{seedfieldBays.jpg}
    \caption[Hybrid seed field production field near Rainer, AB]{Hybrid seed field near Rainer, AB, showing the outlines of male and female bays in the foreground, with orange leafcutter bee shelters stationed throughout the field. The linear structure on the horizon is the central-pivot irrigation sprinkler.}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth,keepaspectratio=true]{seedfieldPlots.png}
    \caption[Plot arrangement for surveys in hybrid seed fields]{Plot arrangement for surveys in hybrid seed fields, showing hypothetical arrangement of leafcutter shelters ($\Delta$), and male-fertile (\Hermaphrodite) and female bays (\Female) at 5m from the edge of the field. Plots were placed along a transect (dashed line) from the field edge nearest to the set of honey bee hives. Plots were placed side-by-side in the male bay and edge of the female bay (``edge" plots), and at the 5m and 400m distances, an additional plot was placed in the centre of the female bay (``centre" plots). Note: this figure shows a small section of a much larger circular field.}
\end{figure}

\begin{table}[h]
\caption{Summary of variables used in structural equation models.}
\centering
\begin{tabular}{l|l|r|r|r|r|r}
\hline
Field Type & Variable & Mean & Median & SD & Min & Max\\
\hline
 & Number of hives & 14.80 & 0.00 & 17.03 & 0.00 & 40.00\\
\cline{2-7}
 & Distance to edge (m) & 137.48 & 20.00 & 195.02 & 1.00 & 500.00\\
\cline{2-7}
 & HB visitation (hr$^{-1}$) & 10.31 & 0.00 & 28.80 & 0.00 & 218.18\\
\cline{2-7}
 & Flower density (m$^2$) & 470.33 & 448.00 & 231.32 & 52.00 & 1684.00\\
\cline{2-7}
 & Pollen per stigma & 293.33 & 155.00 & 385.04 & 0.00 & 3891.00\\
\cline{2-7}
 & Plant density (m$^2$) & 3.77 & 3.77 & 0.48 & 1.79 & 5.02\\
\cline{2-7}
 & Plant vegetative mass (g) & 18.15 & 14.32 & 14.07 & 0.77 & 107.66\\
\cline{2-7}
 & Plant seed mass (g) & 6.87 & 5.46 & 5.97 & 0.01 & 47.90\\
\cline{2-7}
 & Harvest index (g/g) & 0.38 & 0.37 & 0.16 & 0.00 & 1.89\\
\cline{2-7}
 & Flowers per plant & 196.09 & 156.50 & 150.96 & 13.00 & 1094.00\\
\cline{2-7}
 & Pods per plant & 143.15 & 112.00 & 114.64 & 5.00 & 892.00\\
\cline{2-7}
 & Seeds per pod & 22.96 & 23.60 & 4.97 & 4.60 & 35.40\\
\cline{2-7}
\multirow{-13}{*}{\raggedright\arraybackslash Commodity} & Seed size (mg) & 2.74 & 2.73 & 0.80 & 0.39 & 5.35\\
\cline{1-7}
 & Distance to edge (m) & 162.70 & 100.00 & 146.18 & 3.00 & 400.00\\
\cline{2-7}
 & Distance to LCB shelter (m) & 33.51 & 31.00 & 24.63 & 2.00 & 190.00\\
\cline{2-7}
 & HB visitation (hr$^{-1}$) & 112.79 & 24.00 & 187.30 & 0.00 & 1290.00\\
\cline{2-7}
 & LCB visitation (hr$^{-1}$) & 76.15 & 12.00 & 144.88 & 0.00 & 1272.00\\
\cline{2-7}
 & Bay Edge/Centre & 0.13 & 0.00 & 0.34 & 0.00 & 1.00\\
\cline{2-7}
 & Flower density (m$^2$) & 495.02 & 432.00 & 303.35 & 24.00 & 2686.40\\
\cline{2-7}
 & Pollen per stigma & 21.76 & 7.00 & 42.53 & 0.00 & 578.00\\
\cline{2-7}
 & Plant density (m$^2$) & 3.58 & 3.64 & 0.46 & 2.40 & 4.49\\
\cline{2-7}
 & Plant vegetative mass (g) & 30.32 & 25.19 & 21.16 & 1.18 & 144.32\\
\cline{2-7}
 & Plant seed mass (g) & 9.50 & 7.54 & 7.90 & 0.02 & 60.77\\
\cline{2-7}
 & Harvest index (g/g) & 0.32 & 0.33 & 0.15 & 0.00 & 1.21\\
\cline{2-7}
 & Flowers per plant & 461.32 & 362.50 & 326.59 & 26.00 & 2712.00\\
\cline{2-7}
 & Pods per plant & 299.41 & 244.50 & 207.68 & 10.00 & 1410.00\\
\cline{2-7}
 & Seeds per pod & 16.40 & 16.60 & 5.52 & 1.80 & 30.60\\
\cline{2-7}
\multirow{-15}{*}{\raggedright\arraybackslash Seed} & Seed size (mg) & 3.43 & 3.42 & 0.88 & 1.04 & 5.59\\
\hline
\end{tabular}
\end{table}

@@

\begin{table}[h]
  \caption{Number of flower visitors recorded over a total of 44.8 hours of observation in commodity fields (2014 and 2015), and 46.9 hours of observation in the seed fields (2015 and 2016). ``Fly" refers to larger calyptrate muscoid flies (families Muscidae, Anthomyiidae, Caliphoridae), while ``Hover fly" refers to Syrphid flies. ``Other bee" included Halictid and Andrenid bees, while ``Bumble bee" was \textit{Bombus} spp. ``Butterfly" refers to all visiting Lepidopterans, mostly Pierids.}
  \centering
    \begin{tabular}{r|r|l|r|l}
     & \multicolumn{2}{c|}{Commodity fields} & \multicolumn{2}{c}{Seed fields} \\ \cline{2-5}
    Taxon & Visits & \% & Visits & \% \\ \hline
    Honey bee & 470 & 53.5 & 4850 & 77.1 \\
    Fly & 222 & 25.3 & 74 & 0.878 \\
    Hover fly & 94 & 10.7 & 151 & 1.79 \\
    Other bee & 47 & 5.35 & 30 & 0.356 \\
    Bumble bee & 25 & 2.85 & 0 & 0 \\
    Butterfly & 16 & 1.82 & 0 & 0 \\
    Leafcutter bee & 4 & 0.456 & 1675 & 19.9 \\
    % \hline
    % Total & 828 & - & 6780 & - \\
    \end{tabular}
\end{table}

\begin{table}[h]
\caption[Foraging behaviours of honey bees on commodity and seed canola flowers]{Foraging behaviours of honey bees on commodity and seed canola flowers, recorded during 2015. ``Top" (top-working) indicates that the bee inserted their proboscis down between the petals from the top of the flower, while ``side" (side-working) indicates that the bee fed from the side of the flower and did not contact the anthers or stigma. Pollen foragers had pollen visible on their corbicula, while nectar foragers had none.}
\begin{tabular}{r|r|l|r|l|r|l}
               & \multicolumn{2}{c|}{Commodity fields} & \multicolumn{2}{c|}{Seed fields (female bay)} & \multicolumn{2}{c}{Seed fields (male bay)} \\ \cline{2-7}
               & Top & Side & Top & Side & Top & Side           \\ \hline
Pollen forager & 44 & 2 & 12 & 0 & 115 & 0 \\
Nectar forager & 75 & 138 & 832 & 24 & 428 & 242 \\
% Total & 119 & 140 & 844 & 24 & 543 & 242
\end{tabular}
\end{table}

@@

@@

@@

\bibliographystyle{humanbio}
\begin{thebibliography}{}

\bibitem[\protect\astroncite{Free and Ferguson}{1983}]{free1983}
Free, J.~B. and Ferguson, A.~W. 1983.
\newblock Foraging behaviour of honeybees on oilseed rape.
\newblock {\em Bee World}, 64(1):22--24.

\bibitem[\protect\astroncite{Free and Williams}{1973}]{free1973}
Free, J.~B. and Williams, I.~H. 1973.
\newblock The foraging behaviour of honeybees (\emph{Apis mellifera} {L.}) on
  brussels sprout (\emph{Brassica oleracea} {L.}).
\newblock {\em Journal of Applied Ecology}, 10(2):489--499.

\bibitem[\protect\astroncite{Mohr and Jay}{1988}]{mohr1988}
Mohr, N.~A. and Jay, S.~C. 1988.
\newblock Nectar- and pollen-collecting behaviour of honeybees on canola
  (\emph{Brassica campestris} {L}. and \emph{Brassica napus} {L}.).
\newblock {\em Journal of Apicultural Research}, 27(2):131--136.

\end{thebibliography}

\end{document}
